---
title: "test"
author: "Nicholas Nagle"
date: "January 26, 2015"
output: html_document
---
# INSTRUCTIONS:
Edit this file by replacing the instructions with text and code to anser the questions.
I should be able to knit this file and reproduce the html, pdf, or word document.

A block to load in the data:
```{r}
rm(list=ls()) # Clean the workspace to be empty
arbuthnot <- read.csv('~/Documents/Spring Semester 2015//Stastical Geography //jfornade github//jfornade/homework1/data/arbuthnot.csv')
```

# Question 1
This is a question about how the axes affects how we interpret plots.

Create two plots of Male-Female Christenings, one in which the y-axis scale is set by default, and one in which the y-axis extends all the way to zero.  Yes, I know that was in the tutorial.  I want to see it here.
```{r}
library(ggplot2)
ggplot(data=arbuthnot) + geom_line(aes(x=Year, y=Males, color='Male')) + geom_line(aes(x=Year, y=Females, color='Females')) + ylab('Christenings')

ggplot(data=arbuthnot) + geom_line(aes(x=Year, y=Males, color='Male')) + geom_line(aes(x=Year, y=Females, color='Female')) + ylab('Christenings') + scale_y_continuous(limits=c(0, 9000))
```
 
 - Describe the visual appearance of the two plots.  Do they "feel" like they describe the same data?  
 - Describe how you might be able to mislead readers by changing the scaling on graphs.  
 - Which plot seems more appropriate here?  Why?

Yes, these two plots do feel like they do describe the same data. They have the same line, just the one who's limit is (0, 9000) is more compressed in comparison to the default scale. For this example, if the scale is more spread out (like it is in the second plot) the data looks alot more similair that it actually is. HTe more appropiate graph would be the default settings for the scale becuase it shows the best seperation between the amount of male and female Christenings. 

# Question 2
This question is designed to give you some practice with ggplot as well as describing plots in words.

Use ggplot to create a scatterplot that has Female christenings on the x-axis and Male christenings on the y-axis.  Draw a 45 degree line (using geom_abline) to show the line where Male and Female christenings are equal.  Use this figure to describe the relationship and distribution of Male and Female christenings.
```{r}
 ggplot(data=arbuthnot) + geom_point(aes(x=Females, y=Males)) + geom_abline(intercept=0, slope=1) + ylab('Christenings')
```


The scatter plot shows that there is a strong postive correlation between male and female christenings. 

# Question 3

This is a question about population, sample, representativeness and generalizability.

How do you think the christenings-based sample would compared to a births-based sample?  Similar?  Different?  Why?  Arbuthnot's data probably included most every christening in London during this period; they probably aren't any unreported christenings.  Is this fact important?  Why or why not?  Would a christenings based sample be appropriate now, in the 21st century?  (Hint, this last question is trickier than it might seem.  Think about what causes Male/Female Births, what causes people to christen their children, and any relations or not between these)

  A births-based sample would be completely different becuase, espically during this time, the data would not include a very importnt fact: infantile deaths. They would not christen babies unless they have survived long enough to actually perform the cermemony. 
  The fact that Arbuthnot recorded every christening in London is very important beucase it shows that we do not have to make estimations based off of his data. His data incorporates an entire population. 
  A christening-based sample would not be appropiate now because there are a large number of people who will not christen their newborns. Therefore, there needs to be another approach that a research needs to take in order to include a representative sample of the population. 

# Question 4
What does "sex ratio at birth" mean?  How does it depend on biology, cuture and technology.  Consider the three cases of 1) late 17th century England, 2) 21st century US, and China under the [one-child policy](http://en.wikipedia.org/wiki/One-child_policy).

  1) "Sex ratio at birth" means the raito between males and females at birth. There are numerous variables that effect the sex ratio of birth. First off, biology effects the ratio. For example, the age of the mother when the baby is convieved is a huge component. In the 17th century, women were giving birth much, much earlier then they are in the 21st century. Second, culture effects the sex ratio and birth rate becasue it influeces the amount of births that there are, and how many children are on average in a family. In China currently, the culture (and government) limits the amount of children allowed in any Chinese family, due to the large overpopulation of their country. Thirdly, technology effects the sex ratio becuase, the better technology gets the lower the infant death rate is. In the United States in the 21st century has some of the best medical technology in the world, allowing the infant death rate to be lower then it would be in the 17th century. 

# Question 5
The purpose of this quetion is to give you a little practice using standard deviation.

a. The average height of young women ages 18-24 is 64.5 in.  The distribution of heights is approximately normal (Gaussian) with a standardard deviation of $\sigma=2.5$.  Complete this sentence: Approximately 95% of women have a height greater than ______ in and less than ______ in.

  Approximately 95% of women have a height greater than 62 inches and less than 67 inches. 
  
# Question 6
The purpose of this question is to help you understand the variance.

The formula for sample variance $\sigma^2$ of a dataset is:
$$\frac{\sum_{i=1}^N (x_i - \bar{x})^2}{N-1}$$
Describe in words what each part of this equation is, and using the concept of "distance" describe what the sample variance measures.

The summation of the all N values, starting at 1. The N values are the difference between x1 and the mean, rasied to the second power, all over the total number observed minus 1. Essentially, it measures the average distance squared. 
